---
title: "HW1_qguo0701"
author: "Qing Guo"
date: "2019/9/3"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part A

1.to learn how to use some popular software such as R, Python to analysis data
2.to learn how to use github to complete a project with co-workers
3.to learn how to draw some beautiful plots and pictures

## Part B
Three density functions

Example1:

$f_{X}(x)=P(X=x)=\left\{\begin{array}{ll}{(1-p)^{x-1} p} & {\text { for } x=1,2, \ldots} \\ {0} & {\text { otherwise. }}\end{array}\right.$

Example2:

$f_{X}(x)=\frac{2}{9}(x+1), \quad-1 \leq x \leq 2$

Examlpe3:

$f_{X}(x)=\frac{4}{\beta^{3} \sqrt{\pi}} x^{2} e^{-x^{2} / \beta^{2}}, \quad 0<x<\infty, \quad \beta>0$

## Problem 3

Replication is desired by many reproducible research and sicentists are now under much pressure to achieve it. As far as I am concerned, it is truely that to ensure some research trials repetition and reproducibility is increasingly important. We can apply the reproducible reseach results to enhancing data processing effeciently, which is a good habit for a time-saver in the long run.

## Problem 4

```{r Nile, echo=FALSE}
hist(Nile)
plot(EuStockMarkets[1:20],type="p")
```