---
title: "HW2_GUO"
author: "Qing Guo"
date: "9.8.2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---


## Problem 3

Version control allows me to manage data and manage software configuration. 
Version control systems enable me to compare files, identify differences, and merge the changes if needed prior to committing any code. 

## Problem 4
a.Sensory data from five operators

```{r}
url<-"https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/Sensory.dat"
a<-read.table(url,header=T,sep=" ",skip=1,fill=T)
for (i in 1:30){
  if (is.na(a[i,6])==TRUE){
    a[i,2:6]=a[i,1:5]
    a[i,1]=floor((i+2)/3)
  }
}
a
```

b.Gold Medal performance
```{r}
url<-"https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat"
a<-read.table(url,sep=" ",skip=1,fill=T)
a=as.data.frame(a)
a1<-a[,1:2]
a2<-a[,3:4]
a3<-a[,5:6]
a4<-a[,7:8]
a1<-as.matrix(a1)
a2<-as.matrix(a2)
a3<-as.matrix(a3)
a4<-as.matrix(a4)
b<-rbind(a1,a2,a3,a4)
b<-b[1:22,]
b<-as.data.frame(b)
colnames(b)<-c("year","long jump")
b
```

c.Brain weight (g) and body weight (kg)
```{r}
url<-"https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat"
a<-read.table(url,sep=" ",skip=1,fill=T)
a1<-a[,1:2]
a2<-a[,3:4]
a3<-a[,5:6]
a1<-as.matrix(a1)
a2<-as.matrix(a2)
a3<-as.matrix(a3)
b<-rbind(a1,a2,a3)
b<-b[1:62,]
b<-as.data.frame(b)
colnames(b)<-c("Body WT","Brain WT")
b
```
d.Triplicate measurements of tomato yield
```{r}
#install.packages("stringr")
library(stringr)
url<-"https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/tomato.dat"
a<-read.table(url,sep="",skip=1,fill=T,comment.char="")
a<-as.data.frame(a)
d<-c()
for (i in 1:2){
  for (j in 1:3){
    bi_j<-a[i,j]
    bi_j<-unlist(str_split(bi_j,","))
    bi_j<-as.numeric(bi_j[1:3])
    d<-c(d,bi_j)
  }
}
b1<-d[1:9]
b2<-d[10:18]
dataframe<-cbind(b1,b2)
colnames(dataframe)<-c("Ife\\#1","PusaEarlyDwarf")
rownames(dataframe)<-c(rep(10000,3),rep(20000,3),rep(30000,3))
dataframe
```
## Problem 5

```{r}
#install.packages("swirl") 
library(swirl)  
install_course("R_Programming_E")  
swirl()  
bye()
# Path to data
.datapath <- file.path(path.package('swirl'), 'Courses',
                       'R_Programming_E', 'Looking_at_Data',
                       'plant-data.txt')
# Read in data
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")

.cols2rm <- c('Accepted.Symbol', 'Synonym.Symbol')
plants <- plants[, !(names(plants) %in% .cols2rm)]
# Make names pretty
names(plants) <- c('Scientific_Name', 'Duration', 'Active_Growth_Period',
                   'Foliage_Color', 'pH_Min', 'pH_Max',
                   'Precip_Min', 'Precip_Max',
                   'Shade_Tolerance', 'Temp_Min_F')
na_plants<-apply(is.na(plants),1,sum)
plants<-plants[-which((na_plants)>0),]
plants<-plants[,c(1,4,5,6)]
plants$PH_Mean<-(plants$pH_Min+plants$pH_Max)/2
plants$Foliage_Color<-factor(plants$Foliage_Color)
plants
aggregate(plants$PH_Mean,by=list(plants$Foliage_Color),FUN=mean)
aggregate(plants$PH_Mean,by=list(plants$Foliage_Color),FUN=sd)
plants.anova<-aov(plants$PH_Mean~plants$Foliage_Color,data=plants)
F<-summary(plants.anova)
F
```
we can find p<0.05, then we can conclude that PH_Mean is influenced by Foliage_color.


